---
title: "Bootstrapping"
author: "Yuxuan Chen"
date: "11/28/2021"
output: html_document
---
**Repeated sampling**: iterative tool
 - what is the variance of estimated intercepts and slopes in repeated different samples?
 
# Bootstrap works well when assumptions are not met and met! (no need to assume normal distribution)


```{r message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

plot the datasets

```{r}
sim_df_const %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")

sim_df_nonconst %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```
```{r}
# assume constant residual variance
lm(y ~ x, data = sim_df_const) %>% broom::tidy()
lm(y ~ x, data = sim_df_nonconst) %>% broom::tidy()
```

### Drawing one bootstrap sample

1. generating boot samples
```{r}
# this function: sets dataframe as the argument, and return a sample from that dataframe drawn with replacement.

boot_sample = function(df) {
  sample_frac(df, replace = TRUE) %>%  # replace with same sample sizes
    arrange(x) # arrange data
}

```

check function:

```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm") +
  ylim(-5, 16)

boot_sample(sim_df_nonconst) %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```
### many samples and analysis

1. Drawing many bootstrap samples

```{r}
boot_straps = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

# check 1st dataframe:
## boot_straps %>% pull(strap_sample) %>% .[[1]] 
```

2. Run analysis on it:

```{r}
boot_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)

boot_results
```
3. distribution of estimated slopes and intercepts

```{r}
boot_results %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

```{r}
boot_results %>% 
  filter(term == "x") %>%  # only focus on intercept
  ggplot(aes(x = estimate)) +
  geom_density()
```

3. bootstrap Confidence Interval:

```{r}
boot_results %>% 
  group_by(term) %>% 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975),
  )
```

### Boptstrap using modelr
simplify:

```{r}
# similar than previous results

sim_df_nonconst %>% 
  bootstrap(1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

 - Does bootstrap also work well when assumptions met? Yes!

### revisit nyc airbnb

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```

```{r}
airbnb_boot_results = 
  nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  drop_na(stars) %>% 
  bootstrap(1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)

airbnb_boot_results %>% 
  group_by(term) %>% 
  summarize(mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

compare this to `lm`:

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  drop_na(stars) %>% 
  lm(price ~ stars, data = .) %>% 
  broom::tidy()
```

```{r}
airbnb_boot_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) +
  geom_density()
```


