---
title: "cross_validation"
author: "Yuxuan Chen"
date: "11/23/2021"
output: html_document
---
**Model selection!**: HOW TO CHOOSE THE  RIGHT MODEL

```{r message = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


### CV “by hand”
How to find the best fit line: cross validation by hand

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```
1. get training and testing datasets:
    Training: 80%, testing: 20% (everything else than training)
    
```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id") # everything in `nonlin_df`, but not in `train_df`, by `id`.
```

2. Fit three models:

```{r}
# linear model:
linear_mod = lm(y ~ x, data = train_df)

# smooth model:
smooth_mod = gam(y ~ s(x), data = train_df)

# wiggly model
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```


 - plot the three fits: 
 **smooth model should do best in terms of prediction accuracy!**
```{r}
train_df %>% 
  add_predictions(linear_mod) %>% #add prediction values
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") # add line that y is prediction values

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") 

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") 
```
 
 - plot the three fits at the same time    
Add predictions to multiple models at the same time:
```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% #add all prediction values
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~ model)
```

3. check prediction accuracy:    
compute root mean squared errors (RMSEs) for each model.   

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df) # smallest, make the best predictions
rmse(wiggly_mod, test_df)
```



