---
title: "cross_validation"
author: "Yuxuan Chen"
date: "11/23/2021"
output: html_document
---
**Model selection!**: HOW TO CHOOSE THE  RIGHT MODEL

```{r message = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


### Cross validation - "by hand"
How to find the best fit line: 

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```
1. get training and testing datasets:
    Training: 80%, testing: 20% (everything else than training)
    
```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id") # everything in `nonlin_df`, but not in `train_df`, by `id`.
```

2. Fit three models:

```{r}
# linear model:
linear_mod = lm(y ~ x, data = train_df)

# smooth model:
smooth_mod = gam(y ~ s(x), data = train_df)

# wiggly model
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```


 - plot the three fits: 
 **smooth model should do best in terms of prediction accuracy!**
```{r}
train_df %>% 
  add_predictions(linear_mod) %>% #add prediction values
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") # add line that y is prediction values

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") 

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") 
```
 
 - plot the three fits at the same time    
Add predictions to multiple models at the same time:
```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% #add all prediction values
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~ model)
```

3. check prediction accuracy:    
compute root mean squared errors (RMSEs) for each model.   

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df) # smallest, make the best predictions
rmse(wiggly_mod, test_df)
```

### Cross validation - using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) # 100 cross validation
# with training dataset and testing dataset and id
```

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble() # 1st dataset in training
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble()
```

1. convert all objects to tibble:
 
```{r}
# have to do this!!!!
cv_df = 
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```
2. fit models and get RMSEs for them:

```{r}
cv_df = 
  cv_df %>% 
  mutate( 
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod  = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)), #compute rmse for test and model (map2_dbl: number)
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_mod, .y = test, ~rmse(model = .x, data = .y)))
```
 
3. choose the model by rmse:

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()

# linear model is worst; smooth model is better on average in general
```

4.  compute averages:
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(
    ave_rmse = mean(rmse))
```

### try on real dataset
1. import data
```{r}
child_growth_df = 
  read_csv("./data/nepalese_children.csv") %>% 
  mutate(
    weight_cp = (weight > 7) * (weight - 7)
  )
```

2. weight vs arm circumference

```{r}
child_growth_df %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3)
```
3. fit the models I care
```{r}
linear_mod = lm(armc ~ weight, data = child_growth_df)
pwlin_mod = lm(armc ~ weight + weight_cp, data = child_growth_df) # piecewise linear model
smooth_mod = gam(armc ~ s(weight), data = child_growth_df)

```

```{r}
child_growth_df %>% 
  gather_predictions(linear_mod, pwlin_mod, smooth_mod) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~ model)
```

4. compute rmse; understand model fit using CV.
```{r}
cv_df = 
  crossv_mc(child_growth_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(armc ~ weight, data = .x)),
    pwlin_mod = map(.x = train, ~lm(armc ~ weight + weight_cp, data = .x)),
    smooth_mod = map(.x = train, ~gam(armc ~ s(weight), data = .x))) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)), #compute rmse for test and model (map2_dbl: number)
    rmse_pwlin = map2_dbl(.x = pwlin_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)))
```

5. violin plot of RMSEs 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()

# piecewise linear model is better: there is a clear improvement from linear model to piecewise linear model. And the interpretation of piecewise linear model is a little bit straight forward than other models. Smooth model is more accurate but more difficult to interpret. 

```





