---
title: "Linear models"
output: github_document
---
```{r }
library(tidyverse)
library(p8105.datasets)

set.seed(1)

#set the figures' size
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

#set the theme of all graphs
theme_set(theme_minimal() + theme(legend.position = "bottom"))

#set color of all graphs
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis" 
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Import data:

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

### Model fitting:

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

1. linear model: whether price as an outcome depends on rating and borough

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Formula specification of lm function: 
 - outcome on the left of the ~ and predictors separated by + on the right. 
 - interactions between variables can be specified using *. 
 - Can also specify an intercept-only model (outcome ~ 1), a model with no intercept (outcome ~ 0 + ...), and a model using all available predictors (outcome ~ .).

2. Let's look at the results:

```{r, include = FALSE}
# not good: 
fit
summary(fit)
summary(fit)$coef
coef(fit)
residuals(fit)
```

Better way:
1). broom package: obtaining a quick summary of the model and for cleaning up the coefficient table.
```{r}
# both create in dataframe: 
## 1):
broom::glance(fit) 

## 2): Better? 
broom::tidy(fit) %>% # in alphabetical order, Boronx as reference group
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough:") # in `term`, change "borough" to "Borough:"
  ) %>% 
  knitr::kable(digits = 3)

```

### Be in control of factor:

1. Change the reference group:

```{r}
# change the reference group to be the most airbnb rentals

nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough), #change borough from character to factor
    room_type = fct_infreq(room_type)
  )
```

look at the plot again:

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
broom::glance(fit)
```

- Hence, previously is comparing brooklyn to the bronx and mahattan to bronx..., now we are comparing brooklyn to manhattan and bronx to mahattan...

### Diagnostics:

1.modelr package can be used to add residuals and fitted values to a dataframe.

1) add residuals based on model fit:
```{r}
# modelr::add_residuals(dataset, model)

nyc_airbnb %>% 
modelr::add_residuals(fit) %>% # modelr::add_residuals(model)
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() + 
  ylim(-500, 1500) # zoom in the plot
  

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~ borough)
```

### Hypothesis tests:

1. t-test for single coefficients by default: 
Indiviual test: comparing each of three borough at a time:

```{r}
fit %>% 
  broom::tidy()
```

2. F-test:
Multiple comparisons: significance of "borough": comparing all three borough at the same time:
```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)
anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

### Nest data, fit models

```{r}
# not good: 
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)
broom::tidy(fit)
```

This is more exploratory but many easier to understand.
```{r}
# Better: 

nyc_airbnb %>% 
  nest(data = -borough) %>% # nest everyghing except borough
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(term != "(Intercept)") %>% 
  select(borough, term, estimate) %>% 
  pivot_wider(
    names_from = "borough",
    values_from = "estimate"
  )
```


Example: shows neighborhood-specific estimates for the coefficients related to room type.
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
   mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(. ~ term) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))

```

### Logistic regression: Binary outcome
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    expensive_apt = as.numeric(price > 500)
  )
```

Fit a logistic regression for the binary outcome: glm()

```{r}
logistic_fit = 
  glm(
    expensive_apt ~ stars + borough, 
    data = nyc_airbnb,
    family = binomial())

logistic_fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough:"),
    estimate = exp(estimate)
  ) %>% 
  select(term, OR = estimate, p.value)
```

```{r}
nyc_airbnb %>% 
  modelr::add_predictions(logistic_fit) %>% 
  mutate(pred = boot::inv.logit(pred)) #inverse logit function
```

