---
title: "Linear models"
output: github_document
---
```{r }
library(tidyverse)
library(p8105.datasets)

set.seed(1)

#set the figures' size
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

#set the theme of all graphs
theme_set(theme_minimal() + theme(legend.position = "bottom"))

#set color of all graphs
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis" 
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Import data:

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

### Fit a model:

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()

# linear model: whether price as an outcome depends on rating and borough
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's look at the results:

```{r, include = FALSE}
fit

summary(fit)
summary(fit)$coef
coef(fit)
residuals(fit)
```

Better way to look at the results:
```{r}
broom::glance(fit) #format in datafram

broom::tidy(fit) %>% # in alphabetical order, Boronx as reference group
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough:") # in `term`, change "borough" to "Borough:"
  ) %>% 
  knitr::kable(digits = 3)

```

### Be in control of factor:

1. Change reference group:

```{r}
# change to make the reference group be the most airbnb rentals

nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough), #change borough from character to factor
    room_type = fct_infreq(room_type)
  )
```

look at the plot again:

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
broom::glance(fit)
```

- Hence, previously is comparing brooklyn to the bronx and mahattan to bronx..., now we are comparing brooklyn to manhattan and bronx to mahattan...

### Diagnostics:

1. residuals based on model fit
```{r}
# modelr::add_residuals(nyc_airbnb, fit) %>% # modelr::add_residuals(dataset, model)

nyc_airbnb %>% 
modelr::add_residuals(fit) %>% # modelr::add_residuals(model)
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() + 
  ylim(-500, 1500) # zoom in the plot
  

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~ borough)
```

### Hypothesis tests"

1. t-test by default: 
indivudual test:
```{r}
fit %>% 
  broom::tidy()
```

2. F-test:

multiple comparisons: significance of "borough": all three... at the same time:
```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)
anova(fit_null, fit_alt) %>% 
  broom::tidy()
```










